### 2023-06-22 paper/sec-introduction.tex
Additional xFitter ref.s to updated versions, added version number, and the profiling ref.s we would use among xFitter developers

The goal of this work is to bridge this gap and quantify
the expected impact of  DIS structure functions from the LHC
neutrino beam on the proton and nuclear PDFs.
%
To this end, we carry out projections for  FASER$\nu$ and SND@LHC based on the full Run III luminosity
as well as for  three of the proposed experiments to be hosted
at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv}: FLArE, AdvSND, and FASER$\nu$2.
%
For each experiment, we determine the expected event yields in bins in $x$, $Q^2$,
and neutrino energy $E_\nu$,
generate pseudo-data for  inclusive and charm 
structure functions, 
and estimate the main systematic uncertainties and their correlation pattern.
%
Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia}
of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh}, cross-checked
with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
%
We also assess their impact on the PDFs of tungsten (target of FASER$\nu$ and SND@LHC)
using the EPPS21 global nuclear PDF fit~\cite{Eskola:2021nhw}
profiled with {\sc\small xFitter}.

>>>>

The goal of this work is to bridge this gap and quantify
the expected impact of  DIS structure functions from the LHC
neutrino beam on the proton and nuclear PDFs.
%
To this end, we carry out projections for  FASER$\nu$ and SND@LHC based on the full Run III luminosity
as well as for  three of the proposed experiments to be hosted
at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv}: FLArE, AdvSND, and FASER$\nu$2.
%
For each experiment, we determine the expected event yields in bins in $x$, $Q^2$,
and neutrino energy $E_\nu$,
generate pseudo-data for  inclusive and charm 
structure functions, 
and estimate the main systematic uncertainties and their correlation pattern.
%
Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web} version 2.2.1, 
cross-checked with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
%
We also assess their impact on the PDFs of tungsten (target of FASER$\nu$ and SND@LHC)
using the EPPS21 global nuclear PDF fit~\cite{Eskola:2021nhw}
profiled with {\sc\small xFitter}.
